---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# spareparts

<!-- badges: start -->

<!-- badges: end -->

**spareparts** is a depot for one-off functions analyzing data through pipelines that will be updated through time. Currently existing pipelines are outlind below:

- Analysis of thermal endurance challenges to measure V02 max (`TEdriftR()`)
- Analysis of metabolic rate from the feild metabolic system (`VO2FMS()`)

## Getting Started

You can install the development version of **spareparts** from
[GitHub](https://github.com/jsalole/spareparts) with `pak()`.

``` r
# install.packages("pak")
pak::pak("jsalole/spareparts")
```

``` {r}
library("spareparts")
```

This will get the package into your R session.

## Examples

```{r}
head(thermal_endure)
data_01 <- TEdriftR(thermal_endure)
head(data_01$VO2max_candidates)
```

```{r}
head(expedata)
head(markers)
data_02 <- VO2FMS(expedata, markers)
head(data_02$VO2_max_candidates)
```


## Authours

- **Jack Salole**  -
  [jsalole](https://github.com/jsalole)

## Acknowledgments

This collection of functions and example datasets has been generated with the support
of colleagues listed below.

- **K. Garvey:** `TEdriftR`, and datasets (thermal_endure)
- **P. Ouyang:** `TEdriftR`
- **F. O’Dacre:** `TEdriftR`
- **A. Eaton:** `VO2FMS`, and datasets (expedata, markers)